---
title: "Exercise 2"
author: "Daniel Shaver"
date: "December 25, 2018"
output: html_document
---
Question 1 - Read in H3K27Ac_Limb_1.txt file and report the number of genomic locations listed in file.
```{r}
homer <- read.csv("Homer_peaks/h3K27Ac_Limb_1_data_only.txt", sep = "\t")
nrow(homer)
```

Question 2 - Make a histogram of the log10 of regions sizes as shown below using base graphics.
```{r}
hist(log10(homer$region.size))
```

Question 3 - Make a density plot of the log10 of regions sizes as shown below using ggplot graphics.
```{r}
ggplot(homer, aes(x = log10(region.size))) + geom_density(fill = "green")

```

Question 5 - Make a boxplot plot of the log10 of findPeaks.Score for each chromosome as shown below using ggplot graphics.

```{r}
ggplot(homer, aes(y = log10(findPeaks.Score), x = chr, fill = chr)) + geom_boxplot() + coord_flip()
```

Question 6 - Export the Homer genomic regions as a BED3 file.

```{r}
library(BSgenome)
export.bed(homer, con = "homer.bed")
```

